### 2018-06-13 Sections/optimising_the_world.tex
Quant opt algs

Classical techniques for attacking optimisation problems, such as the ones presented above, typically come in two flavours:
\begin{itemize}
	\item Heuristics\index{Heuristics}: efficient algorithms that find suboptimal, but satisfactory \textit{approximations} to the solution to a problem. These algorithms are fast and can be efficiently implemented classically, but can have highly variable accuracy in the solution they provide.
	\item Brute-force\index{Brute-force}: use raw computational power to exhaustively work through all the combinatorics of a problem. This is guaranteed to find the optimal solution, but is typically extremely slow and limited to small instances of the problem.
\end{itemize}

@@

\subsection{Quantum enhancement of satisfiability problems}

@@

>>>>

Classical techniques for attacking optimisation problems, such as the ones presented above, typically come in the following flavours:
\begin{itemize}
	\item Heuristics\index{Heuristics}: efficient algorithms that find suboptimal, but satisfactory \textit{approximations} to the solution to a problem. These algorithms are fast and can be efficiently implemented classically, but can have highly variable accuracy in the solution they provide.
	\item Brute-force\index{Brute-force}: use raw computational power to exhaustively work through all the combinatorics of a problem. This is guaranteed to find the optimal solution, but is typically extremely slow and limited to small instances of the problem.
	\item Efficient classical algorithms: in the most ideal scenario, we may not need either of the above, since efficient classical optimisation algorithms may exist. Perhaps the best-known example of this is \textit{linear programming}\index{Linear programming}, whereby the relationships between entities in a system are defined via linear transformations. This class of problems is classically efficient to solve exactly. Clearly this won't solve \textbf{NP}-complete optimisation problems, but there are nonetheless many problems of interest in this category.
\end{itemize}

@@

\subsection{Quantum enhancement}

\subsubsection{Satisfiability problems}

@@

\subsubsection{Other quantum optimisation algorithms}

\comment{Quantum optimisation algorithms}%https://en.wikipedia.org/wiki/Quantum_optimization_algorithms
